\chapter{Acknowledgements}

This Thesis is part of the "\acl{design}" project that has received funding from the \acl{eu}’s Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No 860095. 

I thank:
\begin{itemize}
    \item the Cleanroom Operations Team of the \acl{brnc} for their help and support. 
    \item Cristina Marinez Oliver for the many fruitful discussions and her help during experiments.
    \item Christian Dam Vedel for the many fruitful discussions, and the images that illustrate the band structures of \acs{si}, and \acs{inp} in its wurtzite and zincblende phases.
    \item Markus Scherrer for photoluminescence measurement and guidance during the first months of my Ph.D. 
    \item Michael Stiefel for the \acs{tem_m} imaging. 
    \item Preslav Aleksandrov for the many fruitful discussion on digital image processing and machine learning.
    \item the former MIND and current QTP groups at \acs{ibm} Research Europe- Zurich and their team leads Kirsten Moselund and Heike Riel for the many fruitful discussion and their support in my research.
    \item the Device Modelling and DeepNano groups at the University of Glasgow for their precious input, and their team leader Vihar Georgier for his supervision during my doctorate.
    \item Marilyne Sousa for supervising during my doctorate and training and trusting me with cutting edge characterization tools; and for carrying out \acs{gpa} calculations on \acs{stem_m} images. 
\end{itemize}



